Probing the Deuteron at Very Large Internal Momenta

### 2020-10-13 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v2.tex
updated PRL revised

carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions

@@

Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\

>>>>

carried out at Jefferson Lab (JLab) and Brookhaven National Lab (BNL). In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

@@

Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. \\
